Decentralized autonomous organization to automate governance\\ {\smaller \textbf{Final Draft - UNDER REVIEW}}

### 2016-04-18 paper/Paper.tex
Purchase -> Create/Creation

A problem every DAO has to mitigate is the ability for the majority to rob the minority by changing governance and ownership rules after DAO formation. For example, an attacker with $51\%$ of the tokens, acquired either during the funding period or purchased afterwards, could make a proposal to send all the funds to themselves. Since they would hold the majority of the tokens, they would always be able to pass their proposals.

@@

The main contract is called 'DAO'. It defines the inner workings of the DAO and it derives the member variables and functions from 'Token' and 'TokenCreation'. ‘Token’ defines the inner workings of the DAO Token and ‘TokenCreation’ defines how the DAO token is purchased for ether. In addition to these three contracts, there is the 'ManagedAccount' contract, which acts as a helper contract to store the rewards which are to be distributed to the token holders and the \verb|extraBalance| (see section \ref{TokenPrice}).
The contract 'SampleOffer' (\ref{app:SampleOffer}) is an example of what a proposal from a contractor to the DAO could look like.
\end{multicols}

@@

The address \verb|privateCreation| is used for DAO splits - if it is set to 0, then it is a public Creation, otherwise, only the address stored in \verb|privateCreation| is allowed to purchase tokens.

@@

\subsubsection*{createTokenProxy}
This function creates one unit of the DAO token’s minimum denomination for every wei sent. The price is calculated as $$\Xi_c \cdot 20 / \text{divisor}$$ Here $\Xi_c$ is the amount of wei given in order to purchase tokens, and \verb|divisor| is calculated depending on the time: $20 / P(t)$ , as described in section \ref{TokenPrice}.
The parameter \verb|tokenHolder| defines the receiver of the newly minted tokens.

@@

\subsubsection*{fallback function}
The fallback function is a function without a specific name. It is called when the contract receives a transaction without data (a pure value transfer). There are no direct arguments for this function.
The fallback function will call \verb|createTokenProxy| passing the address of the sender as an argument during the Creation Phase. This will trigger the immediate purchase of tokens. In order to protect users, this function will send the ether received after the end of the Creation Phase back to the sender for a time period of $40$ days. After which this function is repurposed to receive ether as simple deposit to the DAO using the function \verb|receiveEther|.

@@

    /// @notice Create Token with `_tokenHolder` as the initial owner of the Token
    /// @param _tokenHolder The address of the Tokens's recipient
    /// @return Whether the purchase was successful
    function createTokenProxy(address _tokenHolder) returns (bool success);

@@

    /// @notice Create Token with `msg.sender` as the beneficiary
    /// @return Whether the purchase was successful
    function () returns (bool success);

>>>>

A problem every DAO has to mitigate is the ability for the majority to rob the minority by changing governance and ownership rules after DAO formation. For example, an attacker with $51\%$ of the tokens, acquired either during the fueling period or created afterwards, could make a proposal to send all the funds to themselves. Since they would hold the majority of the tokens, they would always be able to pass their proposals.

@@

The main contract is called 'DAO'. It defines the inner workings of the DAO and it derives the member variables and functions from 'Token' and 'TokenCreation'. ‘Token’ defines the inner workings of the DAO Token and ‘TokenCreation’ defines how the DAO token is created by fueling the DAO with ether. In addition to these three contracts, there is the 'ManagedAccount' contract, which acts as a helper contract to store the rewards which are to be distributed to the token holders and the \verb|extraBalance| (see section \ref{TokenPrice}).
The contract 'SampleOffer' (\ref{app:SampleOffer}) is an example of what a proposal from a contractor to the DAO could look like.
\end{multicols}

@@

The address \verb|privateCreation| is used for DAO splits - if it is set to 0, then it is a public Creation, otherwise, only the address stored in \verb|privateCreation| is allowed to create tokens.

@@

\subsubsection*{createTokenProxy}
This function creates one unit of the DAO token’s minimum denomination for every wei sent. The price is calculated as $$\Xi_c \cdot 20 / \text{divisor}$$ Here $\Xi_c$ is the amount of wei given in order to create tokens, and \verb|divisor| is calculated depending on the time: $20 / P(t)$ , as described in section \ref{TokenPrice}.
The parameter \verb|tokenHolder| defines the receiver of the newly minted tokens.

@@

\subsubsection*{fallback function}
The fallback function is a function without a specific name. It is called when the contract receives a transaction without data (a pure value transfer). There are no direct arguments for this function.
The fallback function will call \verb|createTokenProxy| passing the address of the sender as an argument during the Creation Phase. This will trigger the immediate creation of tokens. In order to protect users, this function will send the ether received after the end of the Creation Phase back to the sender for a time period of $40$ days. After which this function is repurposed to receive ether as simple deposit to the DAO using the function \verb|receiveEther|.

@@

    /// @notice Create Token with `_tokenHolder` as the initial owner of the Token
    /// @param _tokenHolder The address of the Tokens's recipient
    /// @return Whether the token creation was successful
    function createTokenProxy(address _tokenHolder) returns (bool success);

@@

    /// @notice Create Token with `msg.sender` as the beneficiary
    /// @return Whether the token creation was successful
    function () returns (bool success);
